Modeling and Validation of Metadata on \\ Highly-Complex Person-Level Data Sets in RDF

### 2015-01-11 paper/paper6/paper6.tex
disco constraints

@@

@@

@@

\footnote{R-91-UNIVERSAL-QUANTIFICATION-ON-PROPERTIES}

@@

An existential class expression ({\em existential restriction} in DL terminology) contains all those individuals that are connected by the property P to an individual x that is an instance of the class C or to literals that are in the data range DR\footnote{R-86-EXISTENTIAL-QUANTIFICATION-ON-PROPERTIES}.

@@

@@

{\em Property Domain} constraints are defined for each Disco object and data property.

@@

@@

@@

@@

@@

{\em Disjoint Classes} state that all of the classes are pairwise disjoint; 
that is, no individual can be at the same time an instance of these disjoint classes\footnote{R-7-DISJOINT-CLASSES}.
\textbf{{\em DISCO-DISJOINT-CLASSES-01}}.All Disco classes are defined to be pairwise disjoint.
The following DL statements holds for each pair of Disco classes:

@@

>>>>

Where appropriate constraint types are related to complementary requirements of the RDF validation requirements database.

We state one Disco constraint for each constraint type.

@@

A minimum cardinality restrictions contains all those individuals that are connected by a property to at least n different individuals/literals 
that are instances of a particular class or data range. If the class is missing, it is taken to be owl:Thing. 
If the data range is missing, it is taken to be rdfs:Literal.
$\geq n R. C$ is a minimum qualified cardinality restriction where $n \in \mathbb{N}$\footnote{{\em R-75-MINIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES} and {\em R-211-CARDINALITY-CONSTRAINTS}}.

@@

An exact cardinality restriction contains all those individuals that are connected by a property to exactly n different individuals that are instances of a particular class or data range. 
If the class is missing, it is taken to be owl:Thing. 
If the data range is not present, it is taken to be rdfs:Literal.
$\geq n R. C \sqcap \leq n R. C $ is an exact qualified cardinality restriction where $n \in \mathbb{N}$\footnote{{\em R-74-EXACT-QUALIFIED-CARDINALITY-ON-PROPERTIES} and {\em R-211-CARDINALITY-CONSTRAINTS}.}.

@@

A universal class expression ({\em value restriction} in DL) contains all those individuals that are connected by an object property only to individuals that are instances of a particular class\footnote{{\em R-91-UNIVERSAL-QUANTIFICATION-ON-PROPERTIES}}.

@@

An existential class expression ({\em existential restriction} in DL terminology) contains all those individuals that are connected by the property P to an individual x that is an instance of the class C or to literals that are in the data range DR\footnote{{\em R-86-EXISTENTIAL-QUANTIFICATION-ON-PROPERTIES}}.

@@

A union class expression contains all individuals that are instances of at least one class $C_{i}$ for 1 $\leq$ i $\leq$ n. 
A union data range contains all tuples of literals that are contained in the at least one data range $DR_{i}$ for 1 $\leq$ i $\leq$ n.
Synonyms of {\em disjunction} are {\em union} and {\em inclusive or}\footnote{{\em R-17-DISJUNCTION-OF-CLASS-EXPRESSIONS} and {\em R-18-DISJUNCTION-OF-DATA-RANGES}}.

@@

{\em Property Domains} ({\em domain restrictions on roles} in DL) restricts the domain of object and data properties.
The purpose is to declare that a given property is associated with a class. 
In OO terms this is the declaration of a member, field, attribute or association. 
$\exists R. \top \sqsubseteq C$ is the object property restriction where $R$ is the object property (role) whose domain is restricted to concept $C$\footnote{{\em R-25-OBJECT-PROPERTY-DOMAIN} and {\em R-26-DATA-PROPERTY-DOMAIN}}.
{\em Property Domain} constraints are defined for each Disco object and data property.

@@

{\em Property Range} ({\em range restrictions on roles} in DL) restricts the range of object and data properties.
$\top \sqsubseteq \forall R . C$ is the range restriction to the object property $R$ (restricted by the concept $C$)\footnote{{\em R-28-OBJECT-PROPERTY-RANGE} and {\em R-35-DATA-PROPERTY-RANGE}}.

@@

{\em Class-Specific Property Range} restricts the range of object and data properties for individuals within a specific context (e.g. class, shape, application profile).
The values of each member property of a class may be limited by their value type, such as xsd:string or foaf:Person\footnote{{\em R-29-CLASS-SPECIFIC-RANGE-OF-RDF-OBJECTS} and {\em R-36-CLASS-SPECIFIC-RANGE-OF-RDF-LITERALS}}.

@@

A subclass axiom ({\em concept inclusion} in DL) states that the class C1 is a subclass of the class C2 - C1 is more specific than C2\footnote{{\em R-100-SUBSUMPTION}}.

@@

{\em Class Equivalence} asserts that two concepts have the same instances.
While synonyms are an obvious example of equivalent concepts, in practice one more
often uses concept equivalence to give a name to complex expressions \cite{Kroetzsch2012}.
Concept equivalence is indeed subsumption from left and right ($A \sqsubseteq B$ and $B \sqsubseteq A$ implies $A \equiv B$)\footnote{{\em R-3-EQUIVALENT-CLASSES}}.

@@

{\em Disjoint Classes} state that all of the classes are pairwise disjoint; 
that is, no individual can be at the same time an instance of these disjoint classes\footnote{{\em R-7-DISJOINT-CLASSES}}.
\textbf{{\em DISCO-C-01}}. All Disco classes are defined to be pairwise disjoint.
The following DL statements holds for each pair of Disco classes:

@@

\subsection{Asymmetric Object Properties}

A property is asymmetric if it is disjoint from its own inverse \cite{Kroetzsch2012}.
An object property asymmetry axiom states that the object property OP is asymmetric - that is, if an individual x is connected by OP to an individual y, then y cannot be connected by OP to x\footnote{{\em R-62-ASYMMETRIC-OBJECT-PROPERTIES}}.

\textbf{{\em DISCO-C-01}}. 
A {\em disco:Variable} may be based on a {\em disco:RepresentedVariable}.
A {\em disco:RepresentedVariable}, however, cannot be based on a {\em disco:Variable}.
This is a kind of mistake may occur as a semantically equivalent object property for the other direction may also be possible ({\em disco:basisOf}).

\begin{DL}
$basedOn \sqcap basedOn^{-} \sqsubseteq \bot$ 
\end{DL}

\subsection{Class-Specific Irreflexive Object Properties}

A property is irreflexive if it is never locally reflexive \cite{Kroetzsch2012}.
An object property irreflexivity axiom states that the object property OP is irreflexive - that is, no individual is connected by OP to itself.

\textbf{{\em DISCO-C-XX}}.
Within the Disco context, {\em skos:Concept}s cannot be related via the object property {\em skos:boader} to themselves.

\begin{DL}
Concept $\sqsubseteq$ $\neg$$\exists$ broader.Self. 
\end{DL}

\textbf{{\em DISCO-C-XX}}.
Within the Disco context, {\em skos:Concept}s cannot be related via the object property {\em skos:narrower} to themselves.

\begin{DL}
Concept $\sqsubseteq$ $\neg$$\exists$ narrower.Self. 
\end{DL}

\subsection{Context-Specific Exclusive OR of Property Groups}

{\em Context-Specific Exclusive OR of Property Groups} corresponds to the requirement:
{\em R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC}.
Exclusive or is a logical operation that outputs true whenever both inputs differ (one is true, the other is false).
Only one of multiple property groups leads to valid data.

\textbf{{\em DISCO-C-XX}}.
Within the context of Disco, skos:Concepts can have either skos:definition (when interpreted as DDI concepts) or skos:notation and skos:prefLabel properties (when interpreted as DDI codes and categories), but not both.

\begin{DL}
Human $\sqsubseteq$ ($\neg$ E $\sqcap$ F) $\sqcup$ (E $\sqcap$ $\neg$ F) \\ 
E $\equiv$ A $\sqcap$ B \\
F $\equiv$ C $\sqcap$ D \\
A $\sqsubseteq$ $\geq$ 1 name . string $\sqcap$ $\leq$ 1 name . string \\
B $\sqsubseteq$ $\geq$ 1 givenName . string $\sqcap$ $\leq$ 1 givenName . string \\
C $\sqsubseteq$ $\geq$ 1 mbox . IRI $\sqcap$ $\leq$ 1 mbox . IRI \\
D $\sqsubseteq$ $\geq$ 1 homepage . Document $\sqcap$ $\leq$ 1 homepage . Document \\
\end{DL}
